Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
update intro

% \input{main-sketch} % TODO: replace with your brilliant paper!
% \input{macros}

@@

In Fig. \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
This means that in the Beta-Binomial setting the datasets will be
half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
equally split in all the $k=3$ bins. Fig. \ref{fig_vs_datasize} shows that  when the
data size increases, the accuracy of $\hexpemech$ and $\expmechd$
decreases. In Fig. \ref{fig_vs_datasize}(a), when the data size is
smaller than 12, $\hexpmech$ outperforms the Laplace mechanism but fails to do so
for bigger datasets. The same happens in as in Fig. \ref{fig_vs_datasize}(b),
we can beat Laplace mechanism when data size is smaller than 15 and
fail otherwise.

>>>>

% \input{main-sketch} % TODO: replace with your brilliant paper!
% \input{macros}
\section{Introduction}
\label{sec_intro}
When we publish a posterior belief inferred from a sensitive data set in form of a
distribution, itself can relieve a lot of information about data set. So, we need to noise the posterior belief in order to protect the data set before release it. To be precise, distances over two distributions are used to measure the accuracy rather than distances over just parameters or values when we are noising distributions, for instance, Hellinger distance in our paper. Then we have this intuition that when measuring the accuracy between true posterior belief and noised one
using metrics over distribution (Hellinegr distance), a mechanism based on the same distance can outperforms it based on other distance, $\ell_1$-norm for example. However, current mechanisms are mainly based on $l_1$ norm \cite{zhang2016differential,xiao2012bayesian} regardless of the accuracy metric. That's why we design our exponential mechanism based on a metric over distribution -- for specific, Hellinger distance.

@@

In Fig. \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
This means that in the Beta-Binomial setting the datasets will be
half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
equally split in all the $k=3$ bins. Fig. \ref{fig_vs_datasize} shows that  when the
data size increases, the accuracy of $\hexpmech$ and $\hexpmechd$
decreases. In Fig. \ref{fig_vs_datasize}(a), when the data size is
smaller than 12, $\hexpmech$ outperforms the Laplace mechanism but fails to do so
for bigger datasets. The same happens in as in Fig. \ref{fig_vs_datasize}(b),
we can beat Laplace mechanism when data size is smaller than 15 and
fail otherwise.
